Numerical simulation of the dynamics of the artificial heart valve

### 2015-05-11 citech-2015/Paper-template/paper.tex
Working on the text for citech paper

You are strongly encouraged to use \LaTeXe{} for the
preparation of your camera-ready manuscript together with the
corresponding Springer class file \verb+llncs.cls+. Only if you use
\LaTeXe{} can hyperlinks be generated in the online version
of your manuscript.

The \LaTeX{} source of this instruction file for \LaTeX{} users may be
used as a template. This is
located in the ``authors'' subdirectory in
\url{ftp://ftp.springer.de/pub/tex/latex/llncs/latex2e/instruct/} and
entitled \texttt{typeinst.tex}. There is a separate package for Word
users. Kindly send the final and checked source
and PDF files of your paper to the Contact Volume Editor. This is
usually one of the organizers of the conference. You should make sure
that the \LaTeX{} and the PDF files are identical and correct and that
only one version of your paper is sent. It is not possible to update
files at a later stage. Please note that we do not need the printed
paper.

We would like to draw your attention to the fact that it is not possible
to modify a paper in any way, once it has been published. This applies
to both the printed book and the online version of the publication.
Every detail, including the order of the names of the authors, should
be checked before the paper is sent to the Volume Editors.

\subsection{Checking the PDF File}

Kindly assure that the Contact Volume Editor is given the name and email
address of the contact author for your paper. The Contact Volume Editor
uses these details to compile a list for our production department at
SPS in India. Once the files have been worked upon, SPS sends a copy of
the final pdf of each paper to its contact author. The contact author is
asked to check through the final pdf to make sure that no errors have
crept in during the transfer or preparation of the files. This should
not be seen as an opportunity to update or copyedit the papers, which is
not possible due to time constraints. Only errors introduced during the
preparation of the files will be corrected.

This round of checking takes place about two weeks after the files have
been sent to the Editorial by the Contact Volume Editor, i.e., roughly
seven weeks before the start of the conference for conference
proceedings, or seven weeks before the volume leaves the printer's, for
post-proceedings. If SPS does not receive a reply from a particular
contact author, within the timeframe given, then it is presumed that the
author has found no errors in the paper. The tight publication schedule
of LNCS does not allow SPS to send reminders or search for alternative
email addresses on the Internet.

In some cases, it is the Contact Volume Editor that checks all the final
pdfs. In such cases, the authors are not involved in the checking phase.

\subsection{Additional Information Required by the Volume Editor}

If you have more than one surname, please make sure that the Volume Editor
knows how you are to be listed in the author index.

\subsection{Copyright Forms}

The copyright form may be downloaded from the ``For Authors"
(Information for LNCS Authors) section of the LNCS Website:
\texttt{www.springer.com/lncs}. Please send your signed copyright form
to the Contact Volume Editor, either as a scanned pdf or by fax or by
courier. One author may sign on behalf of all of the other authors of a
particular paper. Digital signatures are acceptable.

\section{Paper Preparation}

Springer provides you with a complete integrated \LaTeX{} document class
(\texttt{llncs.cls}) for multi-author books such as those in the LNCS
series. Papers not complying with the LNCS style will be reformatted.
This can lead to an increase in the overall number of pages. We would
therefore urge you not to squash your paper.

Please always cancel any superfluous definitions that are
not actually used in your text. If you do not, these may conflict with
the definitions of the macro package, causing changes in the structure
of the text and leading to numerous mistakes in the proofs.

If you wonder what \LaTeX{} is and where it can be obtained, see the
``\textit{LaTeX project site}'' (\url{http://www.latex-project.org})
and especially the webpage ``\textit{How to get it}''
(\url{http://www.latex-project.org/ftp.html}) respectively.

When you use \LaTeX\ together with our document class file,
\texttt{llncs.cls},
your text is typeset automatically in Computer Modern Roman (CM) fonts.
Please do
\emph{not} change the preset fonts. If you have to use fonts other
than the preset fonts, kindly submit these with your files.

Please use the commands \verb+\label+ and \verb+\ref+ for
cross-references and the commands \verb+\bibitem+ and \verb+\cite+ for
references to the bibliography, to enable us to create hyperlinks at
these places.

For preparing your figures electronically and integrating them into
your source file we recommend using the standard \LaTeX{} \verb+graphics+ or
\verb+graphicx+ package. These provide the \verb+\includegraphics+ command.
In general, please refrain from using the \verb+\special+ command.

Remember to submit any further style files and
fonts you have used together with your source files.

\subsubsection{Headings.}

Headings should be capitalized
(i.e., nouns, verbs, and all other words
except articles, prepositions, and conjunctions should be set with an
initial capital) and should,
with the exception of the title, be aligned to the left.
Words joined by a hyphen are subject to a special rule. If the first
word can stand alone, the second word should be capitalized.

Here are some examples of headings: ``Criteria to Disprove
Context-Freeness of Collage Language", ``On Correcting the Intrusion of
Tracing Non-deterministic Programs by Software", ``A User-Friendly and
Extendable Data Distribution System", ``Multi-flip Networks:
Parallelizing GenSAT", ``Self-determinations of Man".

\subsubsection{Lemmas, Propositions, and Theorems.}

The numbers accorded to lemmas, propositions, and theorems, etc. should
appear in consecutive order, starting with Lemma 1, and not, for
example, with Lemma 11.

\subsection{Figures}

For \LaTeX\ users, we recommend using the \emph{graphics} or \emph{graphicx}
package and the \verb+\includegraphics+ command.

Please check that the lines in line drawings are not
interrupted and are of a constant width. Grids and details within the
figures must be clearly legible and may not be written one on top of
the other. Line drawings should have a resolution of at least 800 dpi
(preferably 1200 dpi). The lettering in figures should have a height of
2~mm (10-point type). Figures should be numbered and should have a
caption which should always be positioned \emph{under} the figures, in
contrast to the caption belonging to a table, which should always appear
\emph{above} the table; this is simply achieved as matter of sequence in
your source.

Please center the figures or your tabular material by using the \verb+\centering+
declaration. Short captions are centered by default between the margins
and typeset in 9-point type (Fig.~\ref{fig:example} shows an example).
The distance between text and figure is preset to be about 8~mm, the
distance between figure and caption about 6~mm.

To ensure that the reproduction of your illustrations is of a reasonable
quality, we advise against the use of shading. The contrast should be as
pronounced as possible.

If screenshots are necessary, please make sure that you are happy with
the print quality before you send the files.
\begin{figure}
\centering
\includegraphics[height=6.2cm]{eijkel2}
\caption{One kernel at $x_s$ (\emph{dotted kernel}) or two kernels at
$x_i$ and $x_j$ (\textit{left and right}) lead to the same summed estimate
at $x_s$. This shows a figure consisting of different types of
lines. Elements of the figure described in the caption should be set in
italics, in parentheses, as shown in this sample caption.}
\label{fig:example}
\end{figure}

Please define figures (and tables) as floating objects. Please avoid
using optional location parameters like ``\verb+[h]+" for ``here".

\paragraph{Remark 1.}

In the printed volumes, illustrations are generally black and white
(halftones), and only in exceptional cases, and if the author is
prepared to cover the extra cost for color reproduction, are colored
pictures accepted. Colored pictures are welcome in the electronic
version free of charge. If you send colored figures that are to be
printed in black and white, please make sure that they really are
legible in black and white. Some colors as well as the contrast of
converted colors show up very poorly when printed in black and white.

\subsection{Formulas}

Displayed equations or formulas are centered and set on a separate
line (with an extra line or halfline space above and below). Displayed
expressions should be numbered for reference. The numbers should be
consecutive within each section or within the contribution,
with numbers enclosed in parentheses and set on the right margin --
which is the default if you use the \emph{equation} environment, e.g.,
\begin{equation}
  \psi (u) = \int_{o}^{T} \left[\frac{1}{2}
  \left(\Lambda_{o}^{-1} u,u\right) + N^{\ast} (-u)\right] dt \;  .
\end{equation}

Equations should be punctuated in the same way as ordinary
text but with a small space before the end punctuation mark.

\subsection{Footnotes}

The superscript numeral used to refer to a footnote appears in the text
either directly after the word to be discussed or -- in relation to a
phrase or a sentence -- following the punctuation sign (comma,
semicolon, or period). Footnotes should appear at the bottom of
the
normal text area, with a line of about 2~cm set
immediately above them.\footnote{The footnote numeral is set flush left
and the text follows with the usual word spacing.}

\subsection{Program Code}

Program listings or program commands in the text are normally set in
typewriter font, e.g., CMTT10 or Courier.

\medskip

\noindent
{\it Example of a Computer Program}
\begin{verbatim}
program Inflation (Output)
  {Assuming annual inflation rates of 7%, 8%, and 10%,...
   years};
   const
     MaxYears = 10;
   var
     Year: 0..MaxYears;
     Factor1, Factor2, Factor3: Real;
   begin
     Year := 0;
     Factor1 := 1.0; Factor2 := 1.0; Factor3 := 1.0;
     WriteLn('Year  7% 8% 10%'); WriteLn;
     repeat
       Year := Year + 1;
       Factor1 := Factor1 * 1.07;
       Factor2 := Factor2 * 1.08;
       Factor3 := Factor3 * 1.10;
       WriteLn(Year:5,Factor1:7:3,Factor2:7:3,Factor3:7:3)
     until Year = MaxYears
end.
\end{verbatim}
%
\noindent
{\small (Example from Jensen K., Wirth N. (1991) Pascal user manual and
report. Springer, New York)}

>>>>

As it was mentioned before, in this work we using the immersed boundary method \cite{pescin_1977}, which are based on that when fluid flows over a body,
it exerts a normal force on the surface, and if the surface is no-slip, the fluid also exerts a shear force. The surface exerts the same force of opposite sign.
This means that fluid flow around a body can be modeled by a corresponding field of the external body forces \cite{goldstain}.

Accordingly to the immersed boundary method, we will determine the fluid flow in the parallelepiped $\tilde{\Omega}$, which contains $\Omega$.
No-splip conditions are imposed at the boundaries if $\tilde{\Omega}$.
For the computation of the fluid flow we will use rectangular uniform staggered grid $\tilde{\Omega_h}$ with grid spacing $h_x$, $h_y$, $h_z$ and 
staggered arrangement of cells, where the pressure, velocity divergence and concentration are computed at the center of cell, the velocity vector components
and vector of external forces - at the boundaries of cell. To determine the deformation of the surface $\Gamma_1 \cup \Gamma_4$ we will introduce additional
area $\tilde{\Gamma}$ with Lagrangian coordinate system, which is related to the vessel walls and valve leaflets. In the $\tilde{\Gamma}$ we will construct
a new grid $\tilde{\Gamma_h}$, which cells are corresponding to the points at the $\Gamma_1 \cup \Gamma_2$. Algorithm of solution consists of the several steps:
at the grid $\tilde{\Gamma_h}$ we will solve the problem (\ref{eq:navier_stokes:motion})-(\ref{eq:navier_stokes:pressure_conditions}); then we will solve
the convection equation (\ref{eq:convection}), i.e. determine the concentration of mixture and recalculate the density and viscosity. After it we will use
the formulas (\ref{eq:boundary_force}), (\ref{eq:boundary_force_simple}) and (\ref{eq:interaction:velocity}), (\ref{eq:interaction:force}) to determine position of
leaflets and the vessel form.

Differential equation (\ref{eq:boundary_force}), (\ref{eq:convection:conditions}) is solved by the finite difference method.
To solve (\ref{eq:boundary_force}), (\ref{eq:boundary_force_simple}) we will use the splitting on physical factors scheme \cite{belotserkovsky}:
\begin{gather}
    \label{eq:splitting:intermediate_velocity}
    \frac{u^* - u^n}{\triangle t} = - (u^n \cdot \nabla) u^* - \frac{1}{\rho} \nabla \sigma + f^n\\
    \label{eq:splitting:poisson}
    \rho \triangle p^{n+1} - \nabla \rho \cdot p^{n+1} = \frac{\rho^2 \nabla u^*}{\triangle t}\\
    \label{eq:splitting:velocity}
    \frac{u^{n+1} - u^*}{\triangle t} = - \frac{1}{\rho} \triangle p^{n+1}
\end{gather}

Computational implementation of this scheme consists of 3 stages. At the beginning the intermediate field $u^*$  is computed from the known values of velocity
from the previous time step. For this equation (\ref{eq:splitting:intermediate_velocity}) is solved by the method of stabilizing corrections \cite{yanenko}.
After it a new pressure field is determined via the computational solution of (\ref{eq:splitting:poisson}) with the biconjugate gradient method usage.
And at the last stage a final velocity vector field is calculated by the formula (\ref{eq:splitting:velocity}).

After fluid flow parameters determining it is necessary to calculate new values of density and velocity. To do that a new time step for the convection
equation (\ref{eq:convection}) must be done using the obtained values of velocity components, and the density and viscosity are recalculated
by the formulas (\ref{eq:viscosity}), (\ref{eq:density}).

Next we need to determine the deformation of vessel walls and valve leaftets under influence of fluid flow, and also the distribution of body forces $f$
in the equation of fluid motion basen on this deformation. We can calculate the deformation of vessel walls and valve leaflets at this particular fluid pressure
and the appearing resistance forces using the equations (\ref{eq:interaction:velocity}) - (\ref{eq:interaction:force}), which are numerically integrated by
the any of quadrature formulas, and equations (\ref{eq:boundary_forces}) - (\ref{eq:boundary_forces_simple}). After it we recalculate the body forces $f$
and go to the next time step.

\section{Results}

We present several results of methodical calculations for the cases of constant and variable density and viscosity, whose purpose is to demonstrate the operability
of the described method and the possibility to get with its help the patterns of  leaflet deformation and mixture distribution inside the valve.
All calculations were performed in dimensionless variables. As a vessel, in which the valve was located, a circular cylinder with length $l = 1$,
radius $r = 0.11$ and wall stiffness $k = 1 \cdot 10^3$ was used, the domain $\tilde{\Omega}$ had the spatial parameters $1.0 \times 0.5 \times 0.5$,
spatial steps $h_x = h_y = h_k = 0.01$, time step $\triangle t = 0.01$.

The dynamics of valve with three leaflets under the influence of the fluid pressure with constans density and velosity is shown in Fig. \ref{fig:valve_1}.
The pressure differential $p_{in} - p_{out}$ changes periodically from 0 to 6. Coefficient of stretching resistanse $k_b = 5 \cdot 10^3$ and coefficient of
bending resistanse $k_b = 5 \cdot 10^3$ are specified for the valve leaflets.

\begin{figure}
\centering
\includegraphics[height=6.2cm]{images/valve_1_gray.png}

$a$

\includegraphics[height=6.2cm]{images/valve_2_gray.png}

$b$

\includegraphics[height=6.2cm]{images/valve_3_gray.png}

$c$

\caption{Extended caption}
\label{fig:valve_1}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=6.2cm]{images/valve_with_particles_1_gray.png}

$a$

\includegraphics[height=6.2cm]{images/valve_with_particles_2_gray.png}

$b$

\includegraphics[height=6.2cm]{images/valve_with_particles_3_gray.png}

$c$

\caption{Scheme of the boundaries of the computational domain}
\label{fig:valve_with_particles_1}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=6.2cm]{images/valves_in_mixture_gray_scale_400.png}

$a$

\includegraphics[height=6.2cm]{images/valves_in_mixture_gray_scale_500.png}

$b$

\includegraphics[height=6.2cm]{images/valves_in_mixture_gray_scale_600.png}

$c$

\caption{Scheme of the boundaries of the computational domain}
\label{fig:valve_in_mixture_1}
\end{figure}
